Functional Analyses of Distinct Oxygen Concentrations and Light Niches of *Prochlorococcus marinus*

### 2024-02-14 Code/Manuscript_O2.Rmd
more mat met edits

```{r PurParPlot, fig.cap = PurParPlot_cap , fig.height = 20, fig.width = 10, echo = FALSE}

@@

Data from the Multicultivators were imported into R-Studio for data
management, growth rate calculations, statistics, and generation of
figures with the `ggplot2` package [@R-tidyverse]. The chlorophyll proxy
optical density (OD680 - OD720) or ΔOD was used to determine the growth
rate for each condition. We used a rolling mean from the RStudio `zoo`
package [@R-zoo] to calculate the average ΔOD data over a 1-hour window.
This was done to prevent extraneous data points from affecting the
growth rate estimates. A Levenberg-Marquardt algorithm
[@bellaviaLevenbergMarquardtMethod2018] modification of the non-linear
least squares fit equation using the R package `minpack.lm`
[@R-minpack.lm] was used to calculate growth rate (µ) using the logistic
equation \@ref(eq:GrowthRate):

```{=tex}
\begin{equation}
  µ = \frac{ΔOD_{max} × ΔOD_{min} × exp^{(µ × t)}}{ΔOD_{max} + (ΔOD_{min} × exp^{((µ × t) - 1)})}
  (\#eq:GrowthRate)
\end{equation}
```
where ΔOD~max~ is maximum ΔOD, ΔOD~min~ is minimum ΔOD, t is time
duration over the growth trajectory.

## Generalized additive model {.unnumbered}

A Generalized Additive Model (GAM) was applied to examine the
relationship between the chlorophyll proxy (ΔOD) growth rate across the
blue spectral waveband, photoperiod and PAR levels for each *P.marinus*
ecotype in this study. The gam function from the R package `mgcv`
[@R-mgcv] was used to model the growth rate with smoothing terms to
indicate the 90, 50 and 10% quantiles. Only data below a standard error
tolerance of 30% of the fit was used in the model. Because of time
limitations, we were unable to conduct sufficient growth response
experiments for all the other spectral wavebands, except for the blue,
to fulfill the input requirements for the GAM. Therefore, our priority
was on studying the effect of blue light on growth trends, considering
that blue light is the most ecologically relevant spectral waveband for
deep ocean niches.

>>>>

### Chlorophyll specific exponential growth rates
Data files saved form from the Multicultivator software were imported into R-Studio (CITATION) for data management [@R-tidyverse], growth rate calculations CITATION, comparisons of model fits CITATION, and generation of
figures`ggplot2` CITATION. The chlorophyll proxy
optical density (OD680 - OD720;  ΔOD) was used to determine the chlorophyll-specific exponential growth
rate (µ, h^-1^) for each treatment combination.  We first we used a rolling mean from the RStudio `zoo` package [@R-zoo] to calculate the average ΔOD data over a 1-hour window, to lower influence of outlier points XXXXother trimmingXXXXX using a Levenberg-Marquardt algorithm
[@bellaviaLevenbergMarquardtMethod2018] modification of the non-linear
least squares,  using the R package `minpack.lm`
[@R-minpack.lm], to fit a logistic
equation \@ref(eq:GrowthRate) where ΔOD~max~ is maximum ΔOD, ΔOD~min~ is minimum ΔOD, t is time
duration over the growth trajectory. 
OTHER MOREXXXXXX

```{=tex}
\begin{equation}
  µ = \frac{ΔOD_{max} × ΔOD_{min} × exp^{(µ × t)}}{ΔOD_{max} + (ΔOD_{min} × exp^{((µ × t) - 1)})}
  (\#eq:GrowthRate)
\end{equation}
```

CITAtIONS of github locations of code etc. XXXXX

### Generalized additive model of growth responses {.unnumbered}

A Generalized Additive Model (GAM) was applied to examine the
relationship between chlorophyll-specific µ, h^-1^, for each [O~2~] level, across the blue and red spectral wavebands, photoperiods and PAR levels for each *P.marinus* strain in this study. The gam function from the R package `mgcv`
[@R-mgcv] was used to model the growth rate with smoothing terms to
indicate the 90, 50 and 10% quantiles for growth rate across the levels of factors. Only data  XXXXXWHAT DATAXXXX BE SPECIFICXXXX below a standard error tolerance of 30% of the fit was used in the model. Our priority
was studying the effect of blue light on growth trends, since blue light is the most ecologically relevant spectral waveband for
deep ocean niches.  We included analyses of responses of red light, which is not ecophysiologically relevant but might prove mechanistically informative (CITE MURPHY ETC)

### Estimation of Photosynthetically Usable Radiation

XXXXTEXT NEEDEDXXXX
```{r PurParPlot, fig.cap = PurParPlot_cap , fig.height = 20, fig.width = 10, echo = FALSE}

@@
